---
title: "Assignment_B2"
author: "Han Wang"
date: "2023-11-08"
output: github_document
Roxygen: list(markdown = TRUE)
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignmentB2Han

<!-- badges: start -->
<!-- badges: end -->

Given a data frame `data` and a ' column `group`, `count_all_missing_by_group()` creates a new data frame with one row per level of `group`. The first column of the output data frame contains the levels of `group`, and the rest of the columns contain the number of missing values for all columns in `data` except `group`. This function is a wrapper around the `group_by()` and `summarize()` functions in the `dplyr` package. 


## Installation

You can install the development version of assignmentB2Han from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/assignmentB2Han", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(assignmentB2Han)
## basic example code
example1 <- count_all_missing_by_group(airquality, Month)
print(example1)
example2 <- airquality |> count_all_missing_by_group(Month)
print(example2)
example3 <- count_all_missing_by_group(airquality, Month, .groups = "keep")
print(example3)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

After installing the package, you can also access the full documentation with:
```{r}
?count_all_missing_by_group
```

